Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-24 method.tex
Fixed typo
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1155 ccdd05d5-56c1-461a-bf98-85f6876523b4

For time slices $s$, the \lloid\ method requires $2 \slicessamps \numsvdtmps f^s$ \flops\ 
to evaluate the orthogonal filters, $2 \numtmps \numsvdtmps f^s$ \flops\ to apply the 
linear transformation from the $\numsvdtmps$ basis templates to the $\numtmps$ time-sliced templates, and $\numtmps f^s$ \flops\ to add the resultant partial \SNR\ stream.

>>>>

For time slice $s$, the \lloid\ method requires $2 \slicessamps \numsvdtmps f^s$ \flops\ 
to evaluate the orthogonal filters, $2 \numtmps \numsvdtmps f^s$ \flops\ to apply the 
linear transformation from the $\numsvdtmps$ basis templates to the $\numtmps$ time-sliced templates, and $\numtmps f^s$ \flops\ to add the resultant partial \SNR\ stream.
